Arrows for Parallel Computations

### 2017-07-08 paper/content/benchmarks.tex

\documentclass[12pt,a4paper]{article}

\usepackage{microtype} %% looks better
\usepackage{pgfplots}

\usepackage{pgfplotstable} %% for regression

\begin{document}

\newcommand{\performanceplot}[5]{
\begin{tikzpicture}
\begin{axis}[title={#1},
title style={align=center},
xlabel=cores,
xtick={#4},
ylabel=time (seconds),
grid=major,
legend entries={#2},
legend pos=outer north east,
xmin=-1,
xmax=#3+1]
#5
\end{axis}
\end{tikzpicture}
}

\newcommand{\speedupplot}[5]{
\begin{tikzpicture}
\begin{axis}[title={#1},
title style={align=center},
xlabel=cores,
xtick={#4},
ytick={#4},
ylabel=speedup,
grid=major,
legend entries={#2},
legend pos=outer north east,
ymin=-1,
xmin=-1,
ymax=#3 + 1,
xmax=#3 + 1]
\addplot [domain=0:#3]{x};
#5
\end{axis}
\end{tikzpicture}
}

\newcommand{\performanceSkelRMSM}[2]{
\performanceplot{Parallel performance of \\ SkelRM #1 #2}{Eden CP, Multicore, ParMonad}{32}{1,4,8,16,32}{
\addplot table [scatter, x="nCores", y="time", col sep=comma, mark=none,
smooth]{benchmarks/sm-rm/bench-sm-rm.bench.skelrm-parr-eden-cp-#1-#2.csv};
\addplot table [scatter, x="nCores", y="time", col sep=comma, mark=none,
smooth]{benchmarks/sm-rm/bench-sm-rm.bench.skelrm-parr-mult-#1-#2.csv};
\addplot table [scatter, x="nCores", y="time", col sep=comma, mark=none,
smooth]{benchmarks/sm-rm/bench-sm-rm.bench.skelrm-parr-par-#1-#2.csv};
}
}

\newcommand{\speedupSkelRMSM}[2]{
\speedupplot{Parallel speedup of \\ SkelRM #1 #2}{Eden CP, Multicore, ParMonad}{32}{1,4,8,16,32}{
\addplot table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{benchmarks/sm-rm/bench-sm-rm.bench.skelrm-parr-eden-cp-#1-#2.csv};
\addplot table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{benchmarks/sm-rm/bench-sm-rm.bench.skelrm-parr-mult-#1-#2.csv};
\addplot table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{benchmarks/sm-rm/bench-sm-rm.bench.skelrm-parr-par-#1-#2.csv};
}
}

@@

\end{document}

>>>>

\section{Benchmarks}
\label{sec:benchmarks}

\newcommand{\performanceplot}[5]{
\begin{tikzpicture}
\begin{axis}[title={#1},
title style={align=center},
xlabel=threads,
xtick={#4},
ylabel=time (seconds),
grid=major,
legend entries={#2},
legend pos=outer north east,
xmin=-1,
xmax=#3+1]
#5
\end{axis}
\end{tikzpicture}
}

\newcommand{\speedupplot}[5]{
\begin{tikzpicture}
\begin{axis}[title={#1},
title style={align=center},
xlabel=threads,
xtick={#4},
ytick={#4},
ylabel=speedup,
grid=major,
legend entries={#2},
legend pos=outer north east,
ymin=-1,
xmin=-1,
ymax=#3 + 1,
xmax=#3 + 1]
\addplot [domain=0:#3]{x};
#5
\end{axis}
\end{tikzpicture}
}

\newcommand{\performanceSkelRMSM}[2]{
\performanceplot{Parallel performance of \\ SkelRM #1 #2}{Eden CP, Multicore, Par Monad}{32}{1,4,8,16,32}{
\addplot table [scatter, x="nCores", y="time", col sep=comma, mark=none,
smooth]{benchmarks/sm-rm/bench-sm-rm.bench.skelrm-parr-eden-cp-#1-#2.csv};
\addplot table [scatter, x="nCores", y="time", col sep=comma, mark=none,
smooth]{benchmarks/sm-rm/bench-sm-rm.bench.skelrm-parr-mult-#1-#2.csv};
\addplot table [scatter, x="nCores", y="time", col sep=comma, mark=none,
smooth]{benchmarks/sm-rm/bench-sm-rm.bench.skelrm-parr-par-#1-#2.csv};
}
}

\newcommand{\speedupSkelRMSM}[2]{
\speedupplot{Parallel speedup of \\ SkelRM #1 #2}{Eden CP, Multicore, Par Monad}{32}{1,4,8,16,32}{
\addplot table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{benchmarks/sm-rm/bench-sm-rm.bench.skelrm-parr-eden-cp-#1-#2.csv};
\addplot table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{benchmarks/sm-rm/bench-sm-rm.bench.skelrm-parr-mult-#1-#2.csv};
\addplot table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{benchmarks/sm-rm/bench-sm-rm.bench.skelrm-parr-par-#1-#2.csv};
}
}

@@
